Wissenschaftliches Arbeiten

### 2014-06-29 review-log.tex
Adding introduction to review log

% TODO: Fill with introduction
% Number in parentheses -> Review Document (1 Unnamed english, 2 german, 3 by Mr Scharinger)

>>>>

The following list contains the suggestions and critic I have got from my colleagues after their peer review. I have corrected most of it, and where I did not, I am explaining why.

The number in parentheses describes who gave me the review. Number 1 the unnamed English one, 2 the unnamed German one, and number 3 is from Mr Scharinger.
